---
title: "S&P Time Series Analysis"
author: "Sagar Sahoo"
date: "18/03/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

Context

Stock market data can be interesting to analyze and as a further incentive, strong predictive models can have large financial payoff. The amount of financial data on the web is seemingly endless. A large and well structured dataset on a wide array of companies can be hard to come by. Here we carry analysis on a dataset with historical stock prices (last 5 years) for all companies currently found on the S&P 500 index.


## R Markdown
```{r}
series_data <- read.csv('all_stocks_5yr.csv')
```

We check the datatypes of the dataframe.

```{r}
str(series_data)
```


```{r}
summary(series_data)
```
```{r}
series_data
```

```{r}
series_data[is.na(series_data)] <- 0

series_data$Date <- as.Date(series_data$Date, format = "%Y-%m-%d")
summary(series_data)

```

```{r}
library('ggplot2')
library('dplyr')
library('tseries')
```

```{r}
i_stock <- filter(series_data, Name == "PSA")
```

```{r}
i_stock
```

```{r}
## Create a daily Date object
inds <- seq(as.Date("2012-08-13"), as.Date("2017-08-11"), by = "day")

create_ts <- function(col_idx){
  ## Create a time series object
  i_ts <- as.numeric(i_stock[,col_idx]) %>%
    tsclean(replace.missing = TRUE, lambda = NULL) %>%
    ts(start = c(2012, as.numeric(format(inds[1], "%j"))),
             frequency = 365.5)
   return(i_ts)
}
```

```{r}
library(forecast)
library(readxl)
#library(stargazer)
#library(fpp)
library(fpp2)
library(scales)
library(quantmod)
library(urca)
library(vars)
library(tseries)
library(ggplot2)
library(dplyr)
```
```{r}
i_stock_ts = create_ts(which(colnames(i_stock) == "High"))
plot.ts(i_stock_ts, xlab = "Time", ylab = "High value", main = "Time Series", col = "red")
```


```{r}
i_tscomponents <- decompose(i_stock_ts)
plot(i_tscomponents, col = "red")
```


```{r}
plot(i_stock_ts)

acf(i_stock_ts)
pacf(i_stock_ts)
```

```{r}
adf.test(i_stock_ts)
```

```{r}
i_tsdiff1 <- diff(i_stock_ts, differences=1)
plot.ts(i_tsdiff1, col = "red")
```
```{r}
adf.test(i_tsdiff1)
```


```{r}
i_tsarima <- auto.arima(i_stock_ts, max.p = 3, max.q = 3, max.d = 3)
i_tsarima
```

```{r}
i_tsforecasts <- forecast(i_tsarima, h = 60)
plot(i_tsforecasts, col = "red")
```

```{r}
plot.ts(i_tsforecasts$residuals)
```

```{r}
ggplot(data.frame(residuals = i_tsforecasts$residuals), aes(residuals)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# make a histogram
```

